Presentation Title

### 2017-06-21 thesis/chapters/ch5-related-work.tex
Change model to pure async

\section{Offchain Transactions}
Offchain transactions make use of the fact that, if two or more parties frequently make transactions,
then it is not necessary to store every transaction on the blockchain, the only useful information is the net settlement.
The best examples are the lightning network~\cite{lightningnetwork} and full duplex channels~\cite{decker2015fast}.
These use the Bitcoin blockchain to store the net settlement and a payment channel to conduct offchain transactions.

TODO explain payment channel

@@

A major side effect of these hybrid systems is that they cannot guarantee correctness when there is a large number of malicious nodes.
Our system has the same issue.
For SCP, ByzCoin and OmniLedger, they all have some probability to elect more than $n$ Byzantine nodes into the committee.
This problem is especially difficult solve because the committee is always much smaller than the population size which has more than $t$ Byzantine nodes,
thus electing more than $t$ nodes into the committee in always a possibility.
Classical blockchain do not have this problem because they do not use Byzantine consensus.
The permissioned systems work around this problem by trusting validators.

>>>>

\section{Offchain Transactions}
Offchain transactions make use of the fact that, if two or more parties frequently make transactions,
then it is not necessary to store every transaction on the blockchain, only the net settlement is necessary.
The best examples are Lightning Network~\cite{lightningnetwork} and full duplex channels~\cite{decker2015fast}.
These use the Bitcoin blockchain to store the net settlement and a payment channel to conduct offchain transactions.

Offchain transaction systems are implemented using multi-signature addresses~\cite{bitcoinmultisig} and Bitcoin contracts.
If two parties wish to make transactions, they open a timelocked payment channel with a multi-signature Bitcoin address (for two parties it would be a 2-of-2 signature address).
Transactions happen off the Bitcoin blockchain and are signed by both parties.
These transactions have a timestamp and only contain the net amount since the start of the payment channel.
Before the payment channel expires, the latest of such transactions is sent to the multi-signature address.
If multiple transactions are sent to the payment channel, the latest one is used.
After payment channel is closed, the net transaction is propagated to the Bitcoin blockchain.

The advantages of such systems is that they act as add-ons to Bitcoin wish already has a large number of users.
Thus, if enough of the network wish for it (by setting a new block version),
then a large number of users will instantly benefit from it.
It also shares the advantages of Bitcoin such as security and incentives.

On the other hand, offchain transactions also suffers from the problem of Bitcoin.
Proof-of-work is still problematic as it consumes an unreasonable amount of power.
TODO more?

@@

A major side effect of these hybrid systems is that they cannot guarantee correctness when there is a large number of malicious nodes.
Our system has the same issue.
For SCP, ByzCoin and Solidus, they all have some probability to elect more than $n$ Byzantine nodes into the committee.
This problem is especially difficult solve because the committee is always much smaller than the population size which has more than $t$ Byzantine nodes,
thus electing more than $t$ nodes into the committee in always a possibility.
Classical blockchain do not have this problem because they do not use Byzantine consensus.
The permissioned systems work around this problem by trusting validators.
